Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Add first conclusion para

>>>>

Retrofitting a type system for the interactive and exploratory programming style
of R is hard. It is even challenging to gain acceptance by the user community.
To this end, we have begun our journey with a simple type language, one that we
believe captures the essence of R while remaining simple and useful. We focus on
the basic language features for generating the type signatures, and find that
